Staged Abstract Interpreters

### 2019-09-11 paper/60_cases.tex
typo

In Section~\ref{sai}, we used a toy language to show that staging an abstract
interpreter is feasible and the artifact can be derived by combining the staged
concrete interpreter and unstaged abstract interpreter.
In this section, we conduct several case studies to further show that this
methodology is practically useful and widely applicable to diverse analyses.

>>>>

In Section~\ref{sai}, we use a toy language to show that staging an abstract
interpreter is feasible and the artifact can be derived by combining the staged
concrete interpreter and unstaged abstract interpreter.
In this section, we conduct several case studies to further show that this
methodology is practically useful and widely applicable to diverse analyses.
